Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
sec 4 updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

To enable the re-use of Ceph subsystems, Malacology relies heavily on
interface classes for introducing new functionality into the MDSs and
OSDs. Malacology introduces 3 components to manage object/metadata
interfaces:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  additional interface hooks and classes for OSDs and MDSs using the
  existing Ceph \texttt{cls} infrastructure
\item
  durable interface classes using the Ceph object store
\item
  versioned and consistent interfaces using the Ceph MONs
\end{enumerate}

@@

Malacogy adds interface hooks to the MDS in the load balancing and
capability subsystems. In contrast to the Mantle implementation, which
had a large function hard-coded into the balancer subsystem, Malacology
embeds code in the MDS using OSD subsystems. Ceph has a whole
infrastructure for getting dynamic code into the OSD. The
\texttt{ClassHandler} class safely opens object interfaces, executes
commands defined by the shared library, and fails gracefully with
helpful errors if anything goes wrong. Instead of injecting strings
directly into Ceph (like we did with the original Mantle
implementation), the \texttt{ClassHandler} class safely opens shared
code, even code with dependencies that are not in Ceph itself (e.g.,
Lua).

@@

Dependencies, symbols, and functions specific to the object or balancer
interface are put in the \texttt{cls} or \texttt{bal} directories,
respectively. For example, the Lua object interface uses functions that
have placement group filters, cryptography functions, and object
metadata (\emph{it i.e.} \texttt{cxx\_omap\_getvals()}, object data,
object extended attributes, and object versions -- all these are
dependencies, symbols, and functions are part of the OSD process but not
the MDS process. As a result, we put interface code that uses these in
\texttt{cls} directory. With this scheme, The OSD will \texttt{dlopen()}
the shared library created by Lua object interface shared library while
the MDS will \texttt{dlopen()} the Lua balancer interface shared
library; both shared libraries will the Lua core.

@@

Both the object and balancer interfaces define functions and attach them
to the core Lua sandbox. For example, the Lua object storage interface
class attaches data, extended attribute, object map, and object version
functions, to the Lua core functions, as shown in Figure
\ref{fig:cls-osd-mds}. The advantages of this is that we avoid
duplicating code, we provide a framework for putting Lua code in other
parts of the system, and we remove components and APIs that are too
integrated with the OSD.

\subsection{Storing Interfaces in
RADOS}\label{storing-interfaces-in-rados}

@@

The cls-lua branch lets users write object classes in Lua, the lua-rados
client library lets users write applications that talk to RADOS with
Lua, and the cls-client uses the lua-rados library to send Lua object
classes to the OSDs equipped with the LuaJIT VM.

>>>>

In this section we describe the extensions to existing Ceph services that
allow for reusability.

{Lua Integration.} Because of limited space we describe our extensions
generally, but we have explicitly added the ability to use Lua to specify
the customizations. Lua is great because..., and let's us save and version
interfaces.

The other two advantages, that Lua leaves a small memory footprint and
that it is secure, are discussed at length in 
\cite{ierusalimschy_programming_2006,neto:dls14-luaos}. In short, Lua
provides relatively robust sandbox capabilities for protecting the

\subsection{Metadata Services}

{\bf Balancing Policy.}
Avoiding hard-coded balancing policies are important. First, it is difficult,
nay impossible, to select a one-size-fits-all policy. System administrators
may want to partition load based on SLAs, etc... Applications are often in
a better position to know what to do.

Mantle is a framework that allows balancing policies to be written in Lua,
and supports such policies be specified at run-time.

{\bf Capabilities.}
The metadata service tracks the state of clients, including the data they
may have cached and any locks that they hold. The metadata service is
responsible responding to client requests for capabilities by first
revoking caps from other clients. Currently clients voluntarily
release their capabilities, and the MDS maintains a queue of requests.
Both clients and MDSs use a best-effort approach to handling capabilities.

In our current we retain the best-effort, volutary release of caps within
clients, but generalize the queueing policies within the MDS to allow for
centeralized policies such as fairness or priority.

{\bf File Types.}
We can reference PDSW12 DataMods, and talk about any new stuff here that we
want to.

\subsection{Object Storage}

Lua integration. Overhead?

Although these OSD interfaces are powerful, the current implementation
has drawbacks. OSD interfaces are written in C/C++ and compiled into a
shared library, so the developer must account for different target
architectures. Second, C/C++ provides more functionality than is
necessary since the snippets of interface code mainly set policies and
perform simple operations. Finally, developing these interfaces in C/C++
has high overhead. The developer must learn how the OSD dynamically

\subsection{Cluster State}

Map modification for propogation of state. We allow applications to augment
these data structures with application-specific metdata. In order to keep the
size of these data structures small application state may be stored elsewhere
and the references stored within the data structure.

\subsection{Programmability and Durability}

{\bf Recovery.}
Application specific recovery is critical.

{\bf Durability.}

\noindent \texttt{ceph\ mds\ set\ lua\_balancer\_class\ \textless{}version\textgreater{}}
\noindent \texttt{ceph\ osd\ pool\ set-class\ \textless{}pool\textgreater{}\ \textless{}class\textgreater{}\ \textless{}script\textgreater{}}

Metadata service policies and object storage interfaces are stored durability
within RADOS and managed by storing references with the object maps. Since
the cluster already propogates a consistent view of these data structures,
we use this service to automatically install interfaces in OSDs, and install
policies within the MDS such that clients and daemons are synchronzied on
correct implementations without restarting.

\iffalse
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  additional interface hooks and classes for OSDs and MDSs using the
  existing Ceph \texttt{cls} infrastructure
\item
  durable interface classes using the Ceph object store
\item
  versioned and consistent interfaces using the Ceph MONs
\end{enumerate}

@@

Malacogy adds interface hooks to the MDS in the load balancing and
capability subsystems. In contrast to the Mantle implementation, which
had a large function hard-coded into the balancer subsystem, Malacology
embeds code in the MDS using OSD subsystems.

Ceph has a whole
infrastructure for getting dynamic code into the OSD. The
\texttt{ClassHandler} class safely opens object interfaces, executes
commands defined by the shared library, and fails gracefully with
helpful errors if anything goes wrong. Instead of injecting strings
directly into Ceph (like we did with the original Mantle
implementation), the \texttt{ClassHandler} class safely opens shared
code, even code with dependencies that are not in Ceph itself (e.g.,
Lua).

@@

Dependencies, symbols, and functions specific to the object or balancer
interface are put in the \texttt{cls} or \texttt{bal} directories,
respectively. For example, the Lua object interface uses functions that
have placement group filters, cryptography functions, and object
metadata (\emph{it i.e.} \texttt{cxx\_omap\_getvals()}, object data,
object extended attributes, and object versions -- all these are
dependencies, symbols, and functions are part of the OSD process but not
the MDS process. As a result, we put interface code that uses these in
\texttt{cls} directory. With this scheme, The OSD will \texttt{dlopen()}
the shared library created by Lua object interface shared library while
the MDS will \texttt{dlopen()} the Lua balancer interface shared
library; both shared libraries will the Lua core.
\fi

@@

\iffalse
Both the object and balancer interfaces define functions and attach them
to the core Lua sandbox. For example, the Lua object storage interface
class attaches data, extended attribute, object map, and object version
functions, to the Lua core functions, as shown in Figure
\ref{fig:cls-osd-mds}. The advantages of this is that we avoid
duplicating code, we provide a framework for putting Lua code in other
parts of the system, and we remove components and APIs that are too
integrated with the OSD.

\subsection{Programmability and Durability}

@@

The cls-lua branch lets users write object classes in Lua, the lua-rados
client library lets users write applications that talk to RADOS with
Lua, and the cls-client uses the lua-rados library to send Lua object
classes to the OSDs equipped with the LuaJIT VM.
\fi
